Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-03-17 manuscript/supplemental_material.Rnw
add more ple-eclampsia genes

@@

>>>>

\subsubsection{Pre-eclampsia genes}

@@

\begin{figure}
<<pappa.evolution.tree,echo=FALSE,fig.width=8,fig.height=8,warning=FALSE,message=FALSE>>=

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="PAPPA" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),
                 gene.tree.table,gene.tree.expression,min.fpkm=5,
                 axis.text.size=5,
                 axis.text.angle=0,
                 fontsize=5
                 )
@ 
\caption{\genetreeexplanation{\textit{PAPPA}}}
\label{fig:pappa_evolution_tree}
\end{figure}

\begin{figure}
<<tgfb1.evolution.tree,echo=FALSE,fig.width=8,fig.height=8,warning=FALSE,message=FALSE>>=

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="TGFB1" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),
                 subtree=c("ENSMODG00000008630","ENSSSCG00000026296"),
                 gene.tree.table,gene.tree.expression,min.fpkm=5,
                 axis.text.size=5,
                 fontsize=5
                 )
@ 
\caption{\genetreeexplanation{\textit{TGFB1}}}
\label{fig:tgfb1_evolution_tree}
\end{figure}
